### 2021-08-22 plos_latex_template.tex
RJ: Edits to communication rule

\section{Rule X: Have an inclusive and diverse organizing team}
\label{organizing_team}
A genuinely inclusive conference can only be organized by an inclusive and diverse organizing team. Build a team with people from different regions, genders, socioeconomic statuses, and other aspects of diversity. Particular attention should be paid to the usually underrepresented groups (see \textbf{Rule 1} discussing the dimensions of diversity lacking in your community and event). To ensure a deeper understanding of the challenges in different diverse groups, it is essential to create a representative working group that functions as a snapshot of the community at large. But this will only work if there is real inclusion. One would be surprised by how often conference leads tend to do everything themselves instead of reaching out to the right people for the right task -- likely because the latter involves careful planning and communication well ahead of time or because they naively overestimate their expertise in areas they lack practical experience in. For example, a cisgender or abled person estimating what might work best for transgender people or people with sensory disabilities. The same holds for other dimensions of diversity. A truly inclusive and welcoming space is one in which everyone in the team is invited and allowed to bring their experience to bear. Even if creating and maintaining such a team and space is challenging, the positive outcomes far outweigh any minor inconveniences (e.g. time zones), and the team will grow, learn, and embrace more inclusive practices \cite{hong_groups_2004}.

@@

Most importantly, accessibility practices are not afterthoughts that can be dealt with at the last minute. 
They require time and early decision-making \cite{irish_increasing_2020}. 
Conversely, inaccessible decisions are hard to course-correct, e.g., when finding out too late that a venue is inaccessible for wheelchairs in an in-person conference. 
Welcoming people that are usually disabled by standard practices in conferences into the organizing team would allow them to take part in the decisions from the beginning and spot right away the inaccessible practices that need to improve (see \textbf{Rule \ref{organizing_team}}).

@@

@@

If some minoritized groups are underrepresented in the conference, they may not feel like they belong. 
If part of the community has been historically discriminated against, one should emphasize that they are particularly welcome in this event and that the organization will make it a safe and inclusive environment. 
An effort must be made to promote the conference as welcoming and supportive for those without the necessary 'credentials' or resources. For the latter, fee waivers, financial support, and ease of application/registration should be advertised. People who are used to applying and getting rejected for scholarships and waivers may find it relieving that the process will be supportive rather than discriminatory against underrepresented groups. Providing financial and other support (e.g., childcare, flexible hours) will help minoritized groups partake more willingly in the organization and the actual conference.
%ast likewise, some key people in your organizing team might not be able to collaborate without remuneration. Resources permitting, it may be a good idea to secure funds to offer stipends to them.

\section{Rule X: Don't let language restrict high-quality participation}

>>>>

\section{Rule X: Have an inclusive and diverse organizing team}
\label{rule_organizing_team}
A genuinely inclusive conference can only be organized by an inclusive and diverse organizing team. Build a team with people from different regions, genders, socioeconomic statuses, and other aspects of diversity. Particular attention should be paid to the usually underrepresented groups (see \textbf{Rule 1} discussing the dimensions of diversity lacking in your community and event). To ensure a deeper understanding of the challenges in different diverse groups, it is essential to create a representative working group that functions as a snapshot of the community at large. But this will only work if there is real inclusion. One would be surprised by how often conference leads tend to do everything themselves instead of reaching out to the right people for the right task -- likely because the latter involves careful planning and communication well ahead of time or because they naively overestimate their expertise in areas they lack practical experience in. For example, a cisgender or abled person estimating what might work best for transgender people or people with sensory disabilities. The same holds for other dimensions of diversity. A truly inclusive and welcoming space is one in which everyone in the team is invited and allowed to bring their experience to bear. Even if creating and maintaining such a team and space is challenging, the positive outcomes far outweigh any minor inconveniences (e.g. time zones), and the team will grow, learn, and embrace more inclusive practices \cite{hong_groups_2004}.

@@

Most importantly, accessibility practices are not afterthoughts that can be dealt with at the last minute. 
They require time and early decision-making \cite{irish_increasing_2020}. 
Conversely, inaccessible decisions are hard to course-correct, e.g., when finding out too late that a venue is inaccessible for wheelchairs in an in-person conference. 
Welcoming people that are usually disabled by standard practices in conferences into the organizing team would allow them to take part in the decisions from the beginning and spot right away the inaccessible practices that need to improve (see \textbf{Rule \ref{rule_organizing_team}}).

@@

\section{Rule X: Don't let language restrict high-quality participation}
\label{rule_language}

@@

If part of the community has been historically discriminated against, one should emphasize that they are particularly welcome in this event and that the organization will make it a safe and inclusive environment. Publish a diversity statement (e.g., \url{https://user2021.r-project.org/about/diversity_statement/}), the code of conduct and accessibility guidelines. Fee waivers, financial support, and ease of application/registration should also be advertised; people who are used to applying and getting rejected for scholarships and waivers may find it relieving that the process will be supportive rather than discriminatory against underrepresented groups. Advertise the conference in multiple languages (rule \ref{rule_language}). Express this welcoming spirit in your communication strategy (social networks, website, brand, and visual identity) to let people know that they are seen, respected, and welcome; that this is their space and community too.

%Providing financial and other support (e.g., childcare, flexible hours) will help minoritized groups partake more willingly in the organization and the actual conference.
%ast likewise, some key people in your organizing team might not be able to collaborate without remuneration. Resources permitting, it may be a good idea to secure funds to offer stipends to them.
